Aggressive Scheduling for Numerical Programs

### 2012-05-02 report/draft.tex
incorporated the graphs

\usepackage{url}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsfonts}   % if you want the fonts
\usepackage{amssymb}    % if you want extra symbols
\usepackage{listings}
%\usepackage{savetrees}

@@

\subsection{Simple Scalar}

\begin{verbatim}
+ What is simplescalar and why are we using it?
+ We want to be able to determine the types of systems that will benefit the
  most from this kind of scheduling.
+ What parameters will we tune?
\end{verbatim}

@@

>>>>

\usepackage{url}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsfonts}   % if you want the fonts
\usepackage{amssymb}    % if you want extra symbols
\usepackage{listings}
%\usepackage{savetrees}
\usepackage{graphicx}

@@

@@

%% I know this is ugly, but if you have the chance Flavio can you beautify
%% this with side-by-side figures
\begin{figure}[ht]
\begin{center}
\includegraphics[scale=.5]{gemv_intel_core_i7_960.png}
\end{center}
\caption{Relative speedup of GEMV on the Intel Core i7 960.}
\label{fig:gemv_corei7}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=.5]{gemv_atom.png}
\end{center}
\caption{Relative speedup of GEMV on the Intel Atom.}
\label{fig:gemv_atom}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=.5]{gemv_core2_extreme_x9650.png}
\end{center}
\caption{Relative speedup of GEMV on the Intel Core2 Extreme X9560.}
\label{fig:gemv_core2}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=.5]{gemv_xeon_e5320.png}
\end{center}
\caption{Relative speedup of GEMV on the Intel Xeon E5320.}
\label{fig:gemv_corei7}
\end{figure}
